---
authors:
categories:
date: "2022-07-12T00:00:00Z"
draft: false
featured: false
image:
  caption: "Methodological overview (part of figure from paper)"
  focal_point: ""
  placement: 2
  preview_only: false
# lastmod: "2021-05-14T00:00:00Z"
projects: []
subtitle: "Overview of the coverage in press, online, and other media"
summary: "Overview of the coverage in press, online, and other media"
tags:
title: "Media coverage: Future Alps paper"
---


The [paper](/research/paper_future_alps) on future snow cover in the European Alps received  international coverage in media, thanks to the help of [GSCC](https://gsccnetwork.org/).

The [report on media coverage](/pdf/Future_Alps_Report_Media_Coverage.pdf) generated by GSCC is available as PDF, as is the [press release](/pdf/PR_Future_Snow_Alps.pdf).

The paper was featured with a [news post](https://www.hydrology-and-earth-system-sciences.net/about/news_and_press/2022-06-21_bias-adjustment-and-downscaling-of-snow-cover-fraction-projections-from-regional-climate-models-using-remote-sensing-for-the-european-alps.html) at the journal homepage, as well as in the [June edition of The Loupe](https://www.egu.eu/newsletter/loupe/90/html/), EGU's newsletter.


Interviews were given to the German and Austrian press agencies, which thus resulted in a wider coverage in those countries. In addition, interviews were requested by a Swiss Radio (RTS), local French newspaper (La Savoie), and a digital Chinese newspaper (The Paper).



Finally, here a non-exhaustive overview of the international media coverage in print and online.



```{r setup, include=FALSE}
library(here)
library(data.table)
library(magrittr)
library(reactable)
```



```{r table, echo=FALSE}

dat <- fread(here("data/press-coverage-future-alps-raw_utf8.csv"), encoding = "UTF-8")
setorder(dat, Date)
dat_sub <- unique(dat[Date != "", 
                      .(Headline, URL, Source, Country, Reach)])

reactable(
  dat_sub,
  filterable = T,
  searchable = T,
  highlight = T,
  paginationType = "jump",
  defaultPageSize = 5,
  style = list(fontSize = "11px"),
  columns = list(
    #Datetime = colDef(minWidth = 100),
    Headline = colDef(minWidth = 200),
    Source = colDef(minWidth = 120),
    Country = colDef(minWidth = 100),
    Reach = colDef(minWidth = 80),
    URL = colDef(
      minWidth = 200,
      html = TRUE,
      cell = JS("function(cell) {
              return '<a href=\"' + cell.value + '\">' + cell.value + '</a>'
                        }")
    )

  )
)
```









